Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-11-13 prob.tex
prob.tex \section{Proofs} lemma:analogLemma3.3Gleason1957 Proved...

\begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ or
$f:\mathbb{C}S^{d-1}\rightarrow\mathbb{R}$ is called a \emph{real}
or \emph{complex approximation frame function} of weight~$\left(W_{l},W_{r}\right)$
if
\begin{itemize}
\item $W_{l}\le\sideset{_{\mathbb{R}}}{_{i=0}^{d-1}}\sum f\left(\ket{\psi_{i}}\right)\le W_{r}$
for any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{d-1}$
of $\mathbb{R}^{d}$ or $\mathbb{C}^{d}$.
\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
$\ket{\psi}\in S^{d-1}$ and $\lambda\in\mathbb{R}\setminus\left\{ 0\right\} $
or $\lambda\in\mathbb{C}\setminus\left\{ 0\right\} $.
\end{itemize}
Also, we will use the same letter $f$ to denote the function defined
on nonzero vector~$\ket{\psi}$ by $f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$
and its unique extension to the whole space~\cite{RichmanBridges1999}.\qed\end{definition}

@@

\begin{thm}\label{thm:analogTheorem21RichmanBridges1999}~ 
\begin{itemize}
\item Let $f:S^{2}\rightarrow\left[0,\infty\right)$ be a continuous\footnote{\yutsung{We need this ``continuous'' to apply Lemma~19 in \cite{RichmanBridges1999},
and need to rewrite Lemma~19 if we want to take away this ``continuous''...}}approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
\item $\ell\left(\ket{\psi}\right)=\ip{0}{\psi}^{2}$ and $Q\left(\ket{\psi}\right)=W\left(1-\ell\left(\ket{\psi}\right)\right)$,
and 
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{thm}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Note that $g_{f,\ket{0}}$
is a nonnegative frame function of weight~$\left(2W_{l},2W_{r}\right)$,
and that $W_{l}-\eta\le g_{f,\ket{0}}\left(\ket{\psi}\right)\le W_{r}-\eta$
for all $\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
the oscillation of $g_{f,\ket{0}}$ on latitudes is at most $\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)$.

@@

For any point $\ket{\psi}$ in the closed northern hemisphere, consider
its longitude~$\varphi$, and a function~$F\left(a\right)=W-g_{f,\ket{0}}\left(\ket{\psi'}\right)$,
where $\ket{\psi'}$ is a point in the closed northern hemisphere
with longitude~$\varphi$, and $a=\ell\left(\ket{\psi'}\right)$.
More specifically, let $\ket{\psi_{i}'}$ be a point in the closed
northern hemisphere with longitude~$\varphi$ such that $a_{i}=\ell\left(\ket{\psi_{i}'}\right)$.
Hence, $\ket{\psi_{i}'}$ and $\ket{\psi_{i}}$ are in the same latitude
so that 
\[
\left|F\left(a_{i}\right)-\left(W-g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)\right)\right|=\left|g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)-g_{f,\ket{0}}\left(\ket{\psi_{i}'}\right)\right|\stackrel{\textrm{Lemma }\ref{lemma:analogLemma20RichmanBridges1999}}{\le}\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)\textrm{ .}
\]
for all $i$. Whence, 
\begin{eqnarray*}
 &  & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-W\right|\\
 & \le & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-3W+g_{f,\ket{0}}\left(\ket{\psi_{0}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{1}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{2}}\right)\right|+\left|2W-\left(g_{f,\ket{0}}\left(\ket{\psi_{0}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{1}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{2}}\right)\right)\right|\\
 & \le & \sum_{i=0}^{2}\left|F\left(a_{i}\right)-W+g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)\right|+\frac{2W_{r}-2W_{l}}{2}\\
 & \le & 3\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+W_{r}-W_{l}\textrm{ .}
\end{eqnarray*}
Therefore, by Lemma~19 in \cite{RichmanBridges1999}, 
\[
\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|=\left|W-g_{f,\ket{0}}\left(\ket{\psi}\right)-W\ell\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\textrm{ .}
\]
\end{proof}
The following theorem is an analog to Corollary~22 in \cite{RichmanBridges1999}.

\begin{cor}\label{thm:analogCorollary22RichmanBridges1999}~
\begin{itemize}
\item Let $f:S^{2}\rightarrow\mathbb{R}$ be a bounded continuous approximation
frame function of weight~$\left(W_{l},W_{r}\right)$, $W=\frac{W_{l}+W_{r}}{2}$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$, $\eta=f\left(\ket{0}\right)-m$, 
\item $Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)$,
and 
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$.\qed\end{cor}
\begin{proof}
Clearly, $f'=f-m$ is a nonnegative frame function of weight~$\left(W_{l}',W_{r}'\right)=\left(W_{l}-3m,W_{r}-3m\right)$
and $W'=\frac{W_{l}'+W_{r}'}{2}=W-3m$. Then, $\eta=f'\left(\ket{0}\right)$
and $g_{f',\ket{0}}=g_{f,\ket{0}}-2m$. Let $Q'\left(\ket{\psi}\right)=Q\left(\ket{\psi}\right)-2m=W'\left(1-\ip{0}{\psi}^{2}\right)$,
and we have $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|=\left|Q'\left(\ket{\psi}\right)-g_{f',\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$
from theorem~\ref{thm:analogTheorem21RichmanBridges1999}.
\end{proof}
Corollary~22 in \cite{RichmanBridges1999} is used to prove theorem~23
which is the final step to prove Gleason's theorem in \cite{RichmanBridges1999}.
Theorem~23 reads as the following.

\begin{thm}\label{thm:analogTheorem23RichmanBridges1999}~
\begin{itemize}
\item Let $f:S^{2}\rightarrow\mathbb{R}$ be a bounded continuous approximation
frame function of weight~$\left(W_{l},W_{r}\right)$, $W=\frac{W_{l}+W_{r}}{2}$, 
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
$\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$.\qed\end{thm}
\begin{proof}
Let $\ket{\bar{2}}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{\bar{0}}$.
Then 
\[
\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{\bar{0}}\right)+f\left(\ket{\bar{2}}\right)\right)\right|\le W_{r}-W_{l}
\]
so
\[
f\left(\ket{\bar{2}}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{\bar{0}}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
\]
whence $f\left(\ket{2}\right)\le m+W_{r}-W_{l}$. Let $\left(x,y,z\right)=\left(\ip{\psi}{0},\ip{\psi}{1},\ip{\psi}{2}\right)$
denote the coordinates of a point~$\ket{\psi}$ with respect to the
frame~$\left\{ \ket{i}\right\} _{i=0}^{2}$, then $Q\left(\ket{\psi}\right)=Mx^{2}+\left(W-M-m\right)y^{2}+mz^{2}$.

@@

In particular, because $\ket{0'}$ is on the great circle~$y'=z'$,
the great circle~$y'=z'$ must intersect the boundary of one of the
previous triangles. Let $\ket{\psi}$ be the intersection, the distance
between $\ket{0'}$ and $\ket{\psi}$ is at most $\frac{1}{\sqrt{3}}$.
That is
\[
\left(1-x'\right)^{2}+2z'^{2}=\left(1-x'\right)^{2}+y'^{2}+z'^{2}\le\frac{1}{3}\textrm{ .}
\]
Also $x'^{2}+2z'^{2}=1$. So $2\left(1-x'\right)\le\frac{1}{3}$ or
$x'\ge\frac{5}{6}$ so $2z'^{2}\le\frac{11}{36}$ whence $x'^{2}-z'^{2}\ge\frac{13}{24}>\frac{1}{2}$.
Now $\left|M'\left(x'^{2}-z'^{2}\right)\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)+\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+3\left(W_{r}-W_{l}\right)\right)$
so 
\begin{eqnarray*}
\left|M'\right| & \le & 3\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)+3\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+3\left(W_{r}-W_{l}\right)\right)\\
 & = & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
\end{eqnarray*}
Same for $m'$, so
\begin{eqnarray*}
\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right| & \le & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
\end{eqnarray*}
\end{proof}
\begin{lemma}\label{lemma:analogLemma3.3Gleason1957}~
\begin{itemize}
\item Let $f:\mathbb{C}S^{1}\rightarrow\mathbb{R}$ be a bounded continuous
approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, 
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
$\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$.\qed\end{lemma}

>>>>

\begin{definition}A function~$f:S^{d-1}\rightarrow\mathbb{R}$ or
$f:\mathbb{C}S^{d-1}\rightarrow\mathbb{R}$ is called a \emph{real}
or \emph{complex approximation frame function} of weight~$\left(W_{l},W_{r}\right)$
if
\begin{itemize}
\item $W_{l}\le\sideset{_{\mathbb{R}}}{_{i=0}^{d-1}}\sum f\left(\ket{\psi_{i}}\right)\le W_{r}$
for any orthonormal basis~$\left\{ \ket{\psi_{i}}\right\} _{i=0}^{d-1}$
of $\mathbb{R}^{d}$ or $\mathbb{C}^{d}$.
\item $f\left(\lambda\ket{\psi}\right)=f\left(\ket{\psi}\right)$ for any
$\ket{\psi}\in S^{d-1}$ and $\lambda\in\mathbb{R}\setminus\left\{ 0\right\} $
or $\lambda\in\mathbb{C}\setminus\left\{ 0\right\} $.
\end{itemize}
Also, we will use the same letter $f$ to denote the function defined
on nonzero vector~$\ket{\psi}$ by $f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$and
$f\left(0\right)=0$~\cite{RichmanBridges1999}.\qed\end{definition}

@@

\begin{thm}\label{thm:analogTheorem21RichmanBridges1999}~ 
\begin{itemize}
\item Let $f:S^{2}\rightarrow\left[0,\infty\right)$ be a continuous\footnote{\yutsung{We need this ``continuous'' to apply Lemma~19 in \cite{RichmanBridges1999},
and need to rewrite Lemma~19 if we want to take away this ``continuous''...}}approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$, $\eta=f\left(\ket{0}\right)$, 
\item $\ell\left(\ket{\psi}\right)=\ip{0}{\psi}^{2}$ and $Q\left(\ket{\psi}\right)=W\left(1-\ell\left(\ket{\psi}\right)\right)$,
and 
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$.\qed\end{thm}
\begin{proof}
Consider $\ket{0}$ to be the north pole of $S^{2}$. Note that $g_{f,\ket{0}}$
is a nonnegative frame function of weight~$\left(2W_{l},2W_{r}\right)$,
and that $W_{l}-\eta\le g_{f,\ket{0}}\left(\ket{\psi}\right)\le W_{r}-\eta$
for all $\ket{\psi}$ on the equator. From Lemma~\ref{lemma:analogLemma20RichmanBridges1999},
the oscillation of $g_{f,\ket{0}}$ on latitudes is at most $\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)$.

@@

For any point $\ket{\psi}$ in the closed northern hemisphere, consider
its longitude~$\varphi$, and a function~$F\left(a\right)=W-g_{f,\ket{0}}\left(\ket{\psi'}\right)$,
where $\ket{\psi'}$ is a point in the closed northern hemisphere
with longitude~$\varphi$, and $a=\ell\left(\ket{\psi'}\right)$.
More specifically, let $\ket{\psi_{i}'}$ be a point in the closed
northern hemisphere with longitude~$\varphi$ such that $a_{i}=\ell\left(\ket{\psi_{i}'}\right)$.
Hence, $\ket{\psi_{i}'}$ and $\ket{\psi_{i}}$ are in the same latitude
so that 
\[
\left|F\left(a_{i}\right)-\left(W-g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)\right)\right|=\left|g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)-g_{f,\ket{0}}\left(\ket{\psi_{i}'}\right)\right|\stackrel{\textrm{Lemma }\ref{lemma:analogLemma20RichmanBridges1999}}{\le}\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)\textrm{ .}
\]
for all $i$. Whence, 
\begin{eqnarray*}
 &  & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-W\right|\\
 & \le & \left|F\left(a_{0}\right)+F\left(a_{1}\right)+F\left(a_{2}\right)-3W+g_{f,\ket{0}}\left(\ket{\psi_{0}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{1}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{2}}\right)\right|\\
 &  & +\left|2W-\left(g_{f,\ket{0}}\left(\ket{\psi_{0}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{1}}\right)+g_{f,\ket{0}}\left(\ket{\psi_{2}}\right)\right)\right|\\
 & \le & \sum_{i=0}^{2}\left|F\left(a_{i}\right)-W+g_{f,\ket{0}}\left(\ket{\psi_{i}}\right)\right|+\frac{2W_{r}-2W_{l}}{2}\\
 & \le & 3\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+W_{r}-W_{l}\textrm{ .}
\end{eqnarray*}
Therefore, by Lemma~19 in \cite{RichmanBridges1999}, 
\[
\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|=\left|W-g_{f,\ket{0}}\left(\ket{\psi}\right)-W\ell\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\textrm{ .}
\]
\end{proof}
The following theorem is an analog to Corollary~22 in \cite{RichmanBridges1999}.

\begin{cor}\label{thm:analogCorollary22RichmanBridges1999}~
\begin{itemize}
\item Let $f:S^{2}\rightarrow\mathbb{R}$ be a bounded continuous approximation
frame function of weight~$\left(W_{l},W_{r}\right)$, $W=\frac{W_{l}+W_{r}}{2}$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)$, $\eta=f\left(\ket{0}\right)-m$, 
\item $Q\left(\ket{\psi}\right)=W-m+\left(3m-W\right)\ip{0}{\psi}^{2}=2m\ip{0}{\psi}^{2}+\left(W-m\right)\left(1-\ip{0}{\psi}^{2}\right)$,
and 
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$.\qed\end{cor}
\begin{proof}
Clearly, $f'=f-m$ is a nonnegative frame function of weight~$\left(W_{l}',W_{r}'\right)=\left(W_{l}-3m,W_{r}-3m\right)$
and $W'=\frac{W_{l}'+W_{r}'}{2}=W-3m$. Then, $\eta=f'\left(\ket{0}\right)$
and $g_{f',\ket{0}}=g_{f,\ket{0}}-2m$. Let $Q'\left(\ket{\psi}\right)=Q\left(\ket{\psi}\right)-2m=W'\left(1-\ip{0}{\psi}^{2}\right)$,
and we have $\left|Q\left(\ket{\psi}\right)-g_{f,\ket{0}}\left(\ket{\psi}\right)\right|=\left|Q'\left(\ket{\psi}\right)-g_{f',\ket{0}}\left(\ket{\psi}\right)\right|\le9\delta\left(\eta,W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)$
from theorem~\ref{thm:analogTheorem21RichmanBridges1999}.
\end{proof}
Corollary~22 in \cite{RichmanBridges1999} is used to prove theorem~23
which is the final step to prove Gleason's theorem in \cite{RichmanBridges1999}.
Theorem~23 reads as the following.

\begin{thm}\label{thm:analogTheorem23RichmanBridges1999}~
\begin{itemize}
\item Let $f:S^{2}\rightarrow\mathbb{R}$ be a bounded continuous approximation
frame function of weight~$\left(W_{l},W_{r}\right)$, $W=\frac{W_{l}+W_{r}}{2}$, 
\item $M=\max_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$,
$m=\min_{\ket{\psi}\in S^{2}}f\left(\ket{\psi}\right)=f\left(\ket{\bar{0}}\right)$, 
\item $\ket{2}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{0}$,
$\ket{1}=\ket{2}\times\ket{0}$, 
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M-m\right)\ip{1}{\psi}^{2}+m\ip{2}{\psi}^{2}$,
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $,
and 
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in S^{2}$..\qed\end{thm}
\begin{proof}
Let $\ket{\bar{2}}=\sigma_{\ket{0}\times\ket{\bar{0}},\frac{\pi}{2}}\ket{\bar{0}}$.
Then 
\[
\left|\left(f\left(\ket{0}\right)+f\left(\ket{2}\right)\right)-\left(f\left(\ket{\bar{0}}\right)+f\left(\ket{\bar{2}}\right)\right)\right|\le W_{r}-W_{l}
\]
so
\[
f\left(\ket{\bar{2}}\right)-f\left(\ket{2}\right)\ge f\left(\ket{0}\right)-f\left(\ket{\bar{0}}\right)-\left(W_{r}-W_{l}\right)=M-m-\left(W_{r}-W_{l}\right)
\]
whence $f\left(\ket{2}\right)\le m+W_{r}-W_{l}$. Let $\left(x,y,z\right)=\left(\ip{\psi}{0},\ip{\psi}{1},\ip{\psi}{2}\right)$
denote the coordinates of a point~$\ket{\psi}$ with respect to the
frame~$\left\{ \ket{i}\right\} _{i=0}^{2}$, then $Q\left(\ket{\psi}\right)=Mx^{2}+\left(W-M-m\right)y^{2}+mz^{2}$.

@@

In particular, because $\ket{0'}$ is on the great circle~$y'=z'$,
the great circle~$y'=z'$ must intersect the boundary of one of the
previous triangles. Let $\ket{\psi}$ be the intersection, the distance
between $\ket{0'}$ and $\ket{\psi}$ is at most $\frac{1}{\sqrt{3}}$.
That is
\left(1-x'\right)^{2}+2z'^{2}=\left(1-x'\right)^{2}+y'^{2}+z'^{2}\le\frac{1}{3}\textrm{ .}
Also $x'^{2}+2z'^{2}=1$. So $2\left(1-x'\right)\le\frac{1}{3}$ or
$x'\ge\frac{5}{6}$ so $2z'^{2}\le\frac{11}{36}$ whence $x'^{2}-z'^{2}\ge\frac{13}{24}>\frac{1}{2}$.
Now $\left|M'\left(x'^{2}-z'^{2}\right)\right|\le\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)+\frac{3}{2}\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+3\left(W_{r}-W_{l}\right)\right)$
so 
\left|M'\right| & \le & 3\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+3\left(W_{r}-W_{l}\right)\right)+3\left(9\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+3\left(W_{r}-W_{l}\right)\right)\\
 & = & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
Same for $m'$, so
\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right| & \le & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
\end{proof}
\begin{lemma}\label{lemma:analogLemma3.3Gleason1957}~
\begin{itemize}
\item Let $f:\mathbb{C}S^{1}\rightarrow\mathbb{R}$ be a bounded continuous
approximation frame function of weight~$\left(W_{l},W_{r}\right)$,
$W=\frac{W_{l}+W_{r}}{2}$. Recall $f$ could be uniquely extended
to the whole space by $f\left(0\right)=0$ and $f\left(\ket{\psi}\right)=\left\Vert \ket{\psi}\right\Vert ^{2}f\left(\left\Vert \ket{\psi}\right\Vert ^{-1}\ket{\psi}\right)$
for nonzero vector~$\ket{\psi}$.
\item $M=\max_{\ket{\psi}\in\mathbb{C}S^{1}}f\left(\ket{\psi}\right)=f\left(\ket{0}\right)$.
\item $\ket{1}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$.
\item $Q\left(\ket{\psi}\right)=M\ip{0}{\psi}^{2}+\left(W-M\right)\ip{1}{\psi}^{2}$.
\item $f'\left(\ket{\psi}\right)=f\left(\ket{\psi}\right)-Q\left(\ket{\psi}\right)$.
\item $\delta\left(\eta,W_{\Delta},\omega_{f}\right)=\sup_{\theta\in\left[0,\frac{\pi}{2}\right)}\min\left\{ \min_{n\ge n\left(\theta\right)}2n\eta+4nW_{\Delta}+2\omega_{f}\left(2-2\cos\left(\frac{\pi^{2}}{n}\right)\right),2\omega_{f}\left(2\cos\theta\right)\right\} $.
\item For any $\ket{1'}\in\mathbb{C}S^{1}$ is orthogonal to $\ket{0}$,
we have $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{1}$ such that $\ip{0}{\psi},\ip{1'}{\psi}\in\mathbb{R}$.
\end{itemize}
Then, $\left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\le27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)$
for all $\ket{\psi}\in\mathbb{C}S^{1}$.\qed\end{lemma}
\begin{proof}
For all $\ket{\psi}\in\mathbb{C}S^{1}$, 
 &  & \left|Q\left(\ket{\psi}\right)-f\left(\ket{\psi}\right)\right|\\
 & = & \left|Q\left(\ket{\psi}\right)-f\left(\ket{0}\ip{0}{\psi}+\ket{1}\ip{1}{\psi}\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\left(\ket{0}\ip{0}{\psi}+\ket{1}\ip{1}{\psi}\right)\right)\right|\\
 & = & \left|Q\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)-f\left(\ket{0}\left|\ip{0}{\psi}\right|+\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\left|\ip{1}{\psi}\right|\right)\right|\\
 & \le & 27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f}\right)+27\delta\left(W_{r}-W_{l},W_{r}-W_{l},\omega_{f'}\right)+18\left(W_{r}-W_{l}\right)
where the last inequality holds because $\ket{1}\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\frac{\ip{1}{\psi}}{\left|\ip{1}{\psi}\right|}\in\mathbb{C}S^{1}$
is orthogonal to $\ket{0}$, $\bra{0}\left(\frac{\left|\ip{0}{\psi}\right|}{\ip{0}{\psi}}\ket{\psi}\right)=1\in\mathbb{R}$,
and 
